MSc Background Report

### 2019-06-03 Report/Progress_Report/Background.tex
work on datasets

\documentclass[12pt]{report}

\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage{indentfirst}
\usepackage{geometry}
 \geometry
 {
     a4paper,
     left=25mm,
     right=25mm,
     top=25mm,
     bottom=25mm,
 }

@@

\chapter{Introduction}

@@

\chapter{Lip Reading}
In recent years the problem of Lip Reading has seen huge advances due to the availability of new datasets and the use of Deep Learning models.
In 2016 the Lip Reading Words (LRW) dataset was published \cite{Chung2016}, followed by Lip Reading Sentences (LRS) in 2017 \cite{Chung2017} and later Large-Scale Visual Speech Recognition (LSVSR) in 2018 \cite{Shillingford2018}, each of which larger in size and resulted in a model which outperforms previous models.
Chung et al \cite{Chung2016} used a convolutional model based on the VGG-M architecture which produced character level distributions with the LRW dataset, these distributions are then processed by a language model for text prediction.
The LRW dataset contains over 1000 hours of spoken text taken from BBC broadcasts, with a over 1000 different speakers, variations in angles and lighting, a vocabulary size of over 1000 words and over one million word utterances.

The LipNet model \cite{Assael2016} was produced to be able to predict sentence-level lip reading of varied length, while previous work by \cite{Chung2016} predicted on a word level.
The model used spatiotemporal convolutions to process multiple frames of video at once followed by a recurrent layer using Gated Recurrent Units (GRU) \cite{Cho2014}.
The model used the GRID dataset which is of a similar size as LRW, but has far less variation in speakers.
LipNet achieved the state of the art performance on the GRID dataset by using an model with increased complexity by incorporating 3D convolution and recurrent units.

@@

\chapter{Data Generation}
\section{Data Capture}
Current lip reading models currently make use of 2D temporal data such as videos.
This is convenient as video data is already widely available and relatively straightforward to process.
The reason for the wide availability of video data is due to the ease of capturing and viewing such data.
Unlike 2D temporal data, 3D temporal data or 3D video, requires multiple cameras to record simultaneously, which requires synchronisation, adding to the complexity of the system.
The data must then be processed to produce the final product, whether this is in the form of video with depth information or more complex 3D scans \cite{Li2017}.

\subsection{2D Datasets}
Due to the large availability of video data, datasets such as LRW, LRS and LSVSR have been constructed by compiling the appropriate data.
LRW and LRS are both comprised of content from BBC broadcasts \cite{Chung2016, Chung2017}

\subsection{3D Datasets}

\subsection{Original Dataset}

@@

\chapter{3D Modelling}
\begin{itemize}
    \item blendshapes
    \item Model Correspondence
\end{itemize}

\chapter{Recurrent Models}
\begin{itemize}
    \item Recurrent networks
    \item LSTMs
    \item Attention Mechanism
\end{itemize}

\chapter{Speech Recognition}
Deep Speech \cite{Karras2017a}

\chapter{Current Work and Future Work}
Data collection

>>>>

\documentclass[12pt]{article}

\usepackage[nottoc,notlot,notlof]{tocbibind}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{indentfirst}
\usepackage{geometry}
 \geometry
 {
     a4paper,
     left=25mm,
     right=25mm,
     top=25mm,
     bottom=25mm,
 }

@@

\section{Introduction}

@@

\section{Lip Reading}
In recent years the problem of Lip Reading has seen huge advances due to the availability of new datasets and the use of Deep Learning models.
In 2016 the Lip Reading Words (LRW) dataset was published \cite{Chung2016}, followed by Lip Reading Sentences (LRS) in 2017 \cite{Chung2017} and later Large-Scale Visual Speech Recognition (LSVSR) in 2018 \cite{Shillingford2018}, each of which larger in size and resulted in a model which outperforms previous models.
Chung et al \cite{Chung2016} used a convolutional model based on the VGG-M architecture which produced character level distributions with the LRW dataset, these distributions are then processed by a language model for text prediction.
The LRW dataset contains over 1000 hours of spoken text taken from BBC broadcasts, with a over 1000 different speakers, variations in angles and lighting, a vocabulary size of over 1000 words and over one million word utterances.

The LipNet model \cite{Assael2016} was produced to be able to predict sentence-level lip reading of varied length, while previous work by \cite{Chung2016} predicted on a word level.
The model used spatiotemporal convolutions to process multiple frames of video at once followed by a recurrent layer using Gated Recurrent Units (GRU) \cite{Cho2014}.
The model used the GRID dataset \cite{Cooke2006} which is of a similar size as LRW, but has far less variation in speakers.
LipNet achieved the state of the art performance on the GRID dataset by using an model with increased complexity by incorporating 3D convolution and recurrent units.

@@

\section{Data Generation}
\subsection{Data Capture}
Current lip reading models currently make use of 2D temporal data such as videos.
This is convenient as video data is already widely available and relatively straightforward to process.
The reason for the wide availability of video data is due to the ease of capturing and viewing such data.
Unlike 2D temporal data, 3D temporal data or 3D video, requires multiple cameras to record simultaneously, which requires synchronisation, adding to the complexity of the system.
The data must then be processed to produce the final product, whether this is in the form of video with depth information or more complex 3D scans \cite{Li2017}.

\subsubsection{2D Datasets}
Due to the large availability of video data, datasets such as GRID \cite{Cooke2006}, LRW \cite{Chung2016}, LRS \cite{Chung2017} and LSVSR \cite{Shillingford2018} have been constructed by compiling the appropriate data.
GRID contains 34,000 samples from 34 speakers, each with 1000 sentences.
The corpus uses sentences with a fixed grammar: 
<command:4>, <colour:4>, <preposition:4>, <letter:25>, <number:10>, <adverb:4>, with a total vocabulary of 51 words.

LRW and LRS are both comprised of content from BBC broadcasts \cite{Chung2016, Chung2017} allowing for a far larger corpus size of over 1000 words for LRW and over 6000 words for LRS.
Both of datasets are captured and processed with the same pipeline summarised as follows. 
Firstly, as the subtitles are not aligned to the video on the broadcasts, optical chapter recognition is used to obtain the text being spoken in the video clips, the audio and text are then aligned per frame using the HTK toolkit \cite{Woodland1995}. 
A HOG-based detection algorithm \cite{King2009} is used for face detection for cropping the frames to the subjects head followed by facial landmarks for mouth localisation and speaker identification. 
\subsubsection{3D Datasets}

\subsubsection{Original Dataset}

@@

\section{3D Modelling}
\begin{itemize}
    \item blendshapes
    \item Model Correspondence
\end{itemize}

\section{Recurrent Models}
\begin{itemize}
    \item Recurrent networks
    \item LSTMs
    \item Attention Mechanism
\end{itemize}

\section{Speech Recognition}
Deep Speech \cite{Karras2017a}

\section{Current Work and Future Work}
Data collection
